Determining the alternatives for scalar implicature

### 2016-01-29 Paper/Paper.Rmd
changed axis title on speakers plot

# Non-summarized data
# -------------------
allLiteralListener <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/RawLiteralListenerCombined.csv")
allPragmaticListener <- read.csv("~/Desktop/Projects/scalar_implicature/models//model_data/RawPragmaticListenerCombined.csv")

@@

# for plotting
speakers$study <- ifelse(speakers$expt == "e8", "1a",
                                 ifelse(speakers$expt == "e10", "1b", "1c"))
ggplot(speakers, 
       aes(x = stars, y = speaker.p, col = study)) + 
  geom_line() + 
  # facet_grid(.~ scale) + 
  facet_wrap(~wordPlots) +
  guides(colour = guide_legend(direction = "horizontal", nrow = 1, 
                               title = "Scalar Item"), 
         linetype = guide_legend(direction = "horizontal", nrow = 1, 
                                 title = "Experiment")) + 
  xlab("star rating") +
  ylab("proportion compatible ('yes' responses)") + 
  # ggtitle("Scalar item literal semantic compatibility\nwith star ratings") +
  # scale_colour_solarized() + 
  theme_bw() +
  theme(strip.text.x = element_text(size = 6),
        legend.position = "bottom",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"),
        legend.title = element_text(size = 10),
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 6))
```

>>>>

# Non-summarized data
# -------------------
allLiteralListener <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/RawLiteralListenerCombined.csv")
allPragmaticListener <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/RawPragmaticListenerCombined.csv")

@@

# for plotting
speakers$study <- ifelse(speakers$expt == "e8", "1a",
                                 ifelse(speakers$expt == "e10", "1b", "1c"))
ggplot(speakers, 
       aes(x = stars, y = speaker.p, col = study)) + 
  geom_line() + 
  # facet_grid(.~ scale) + 
  facet_wrap(~wordPlots) +
  guides(colour = guide_legend(direction = "horizontal", nrow = 1, 
                               title = "Experiment")) + 
  xlab("star rating") +
  ylab("proportion compatible ('yes' responses)") + 
  # ggtitle("Scalar item literal semantic compatibility\nwith star ratings") +
  # scale_colour_solarized() + 
  theme_bw() +
  theme(strip.text.x = element_text(size = 6),
        legend.position = "bottom",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"),
        legend.title = element_text(size = 10),
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 6))
```
